Data Analysis

### 2022-04-08 03.data_analysis.Rmd
updated from meeting

table(o_works$type)

# combine types ####see issues here #### 
# works_df$our_type <- works_df$type
# works_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", works_df$our_type)

@@

s_works_summary <- s_works %>% 
  group_by(scholar) %>% 
  summarize(s_career_1_pub = 2022 - min(year, na.rm = T),
            s_total_pub = n())
####citations??####

####see issues here####
o_ed_summary <- o_ed %>% 
  group_by(ORCID) %>% 
  summarize(o_career_1_degree = 2022 - min(education_summary_end_date_year_value, na.rm = T))

@@

```{r}
table(bibs$JOURNAL)
table(bibs$KEYWORDS)

@@

>>>>

table(o_works$type)
o_works$our_type <- o_works$type
o_works$our_type <- gsub("edited-book|book.+", "book", o_works$our_type)
o_works$our_type <- gsub("conference.+", "conference", o_works$our_type)
o_works$our_type <- gsub("dissertation-thesis|supervised-student.+", "thesis", o_works$our_type)
o_works$our_type <- gsub("magazine.+|report|dictionary-entry", "other-pub", o_works$our_type)
o_works$our_type <- gsub("working-paper", "preprint", o_works$our_type)
o_works$our_type <- gsub("website", "other", o_works$our_type)

table(o_works$our_type)

@@

s_works_summary <- s_works %>% 
  group_by(scholar) %>% 
  summarize(s_career_1_pub = 2022 - min(year, na.rm = T),
            s_total_pub = n())

# remember to ignore inf 
o_ed_summary <- o_ed %>% 
  group_by(ORCID) %>% 
  summarize(o_career_1_degree = 2022 - min(education_summary_end_date_year_value, na.rm = T))

@@

```{r}
table(bibs$JOURNAL)
table(bibs$KEYWORDS) # hand code

#### impact factor grab them now #### 
```

@@

- credit contributions ? are we using de-weirding by using those people for translation and data collection only 
  - grab major roles and see what the diversity is 
  - look at the first 10 people and the last author 
  - maybe compare to the other 10 groups (1/3rd, middle, last 1/3rd)
  - employment_summary_organization_address_country (for the weird part)
  - average career length / publication counts 
- across time 
  - more varied across time
  - more people 
  - more different types of people - education levels, jobs levels, country
  - more citation style things - are people publishing more who are on these teams and what indices do they have
